Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2017-11-29 paper.tex
djfkdjf

The database augmentation step allowed 209 modification types, including PTMs, adducts, and chemical modifications. See Supplementary Table 1 for a complete listing.

@@

%\begin{suppinfo}

%The following files are available free of charge.
%\begin{itemize}
%  \item Filename: brief description
%  \item Filename: brief description
%\end{itemize}

>>>>

The database augmentation step allowed 208 modification types, including PTMs, adducts, and chemical modifications.
See Supplementary Table 1 for a complete listing.

@@

\begin{suppinfo}

The following files are available free of charge.
\begin{itemize}
  \item Supp1.xlsx: The complete list of modifications used for enhanced G-PTM-D
  \item Supp2Calibration.docx: brief description
\end{itemize}
